Dynamics of Laterally Propagating Flames in X-ray Bursts. II. Realistic Burning \& Rotation

### 2021-01-11 xrb2/paper.tex
fix phase plot figure captions

\begin{figure}[t]
    \centering
    \plotone{urho_plot_hotter}
    \caption{\label{fig:urho_hot}Phase plot of the horizontal $x$-velocity $u$, density $\rho$ and the nuclear energy generation rate $\dot{e}_{\rm nuc}$ for the 500~Hz runs with $T_{\rm star}$ of $10^8$~K, $2\times10^8$~K and $3\times10^8$~K at $t = 40$~ms.}
\end{figure}

\begin{figure}[t]
    \centering
    \plotone{uv_plot_hotter}
    \caption{\label{fig:uv_hot}Phase plot of the horizontal $x$-velocity $u$, vertical $y$-velocity $v$ and the nuclear energy generation rate $\dot{e}_{\rm nuc}$ for the 500~Hz runs with $T_{\rm star}$ of $10^8$~K, $2\times10^8$~K and $3\times10^8$~K at $t = 40$~ms.}
\end{figure}

\begin{figure}[t]
    \centering
    \plotone{abar_plot_hotter}
    \caption{\label{fig:abar_hot}Phase plot of the mean molecular weight $\bar{A}$, temperature $T$ and the nuclear energy generation rate $\dot{e}_{\rm nuc}$ for the 500~Hz runs with $T_{\rm star}$ of $10^8$~K, $2\times10^8$~K and $3\times10^8$~K at $t = 40$~ms.}
\end{figure}

>>>>

\begin{figure}[t]
    \centering
    \plotone{urho_plot_hotter}
    \caption{\label{fig:urho_hot}Phase plot of the horizontal $x$-velocity $u$, density $\rho$ and the nuclear energy generation rate $\dot{e}_{\rm nuc}$ for the 500~Hz runs with $T_{\rm star}$ of $10^8$~K, $3\times10^8$~K and $4\times10^8$~K at $t = 40$~ms.}
\end{figure}

\begin{figure}[t]
    \centering
    \plotone{uv_plot_hotter}
    \caption{\label{fig:uv_hot}Phase plot of the horizontal $x$-velocity $u$, vertical $y$-velocity $v$ and the nuclear energy generation rate $\dot{e}_{\rm nuc}$ for the 500~Hz runs with $T_{\rm star}$ of $10^8$~K, $3\times10^8$~K and $4\times10^8$~K at $t = 40$~ms.}
\end{figure}

\begin{figure}[t]
    \centering
    \plotone{abar_plot_hotter}
    \caption{\label{fig:abar_hot}Phase plot of the mean molecular weight $\bar{A}$, temperature $T$ and the nuclear energy generation rate $\dot{e}_{\rm nuc}$ for the 500~Hz runs with $T_{\rm star}$ of $10^8$~K, $3\times10^8$~K and $4\times10^8$~K at $t = 40$~ms.}
\end{figure}
